---
title: "GIS-FINAL"
output: html_document
---

```
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, results='hide'}
#library a bunch of packages first
library(tidyverse)
library(tmap)
library(geojsonio)
library(plotly)
library(rgdal)
library(broom)
library(mapview)
library(crosstalk)
library(sf)
library(sp)
library(spdep)
library(car)
library(fs)
library(janitor)
library(dplyr)
library(fs)
library(here)
library(stringr)
library(utils)
library(highcharter)
library(downloader)
library(rgdal)
library(ggplot2)
library(reshape2)
library(plotly)
library(raster)
library(grid)
library(Rmisc)
```

#**Part 1：Aggregate and clean data**

##1.1 Ward boundary
```{r setup, results='hide'}
#download a zip file containing some boundaries

download.file("https://data.london.gov.uk/download/statistical-gis-boundary-files-london/9ba8c833-6370-4b11-abdc-314aa020d5e0/statistical-gis-boundaries-london.zip", destfile="data/statistical-gis-boundaries-london.zip")
#if download not work well, please download manually

#Get the zip file and extract it
listfiles<-dir_info(here::here("data")) %>%
  dplyr::filter(str_detect(path, ".zip")) %>%
  dplyr::select(path)%>%
  pull()%>%
  #print out the .gz file
  print()%>%
  as.character()%>%
  utils::unzip(exdir=here::here("data"))
#look what is inside the zip
Londonwards<-dir_info(here::here("data", 
                                 "statistical-gis-boundaries-london", 
                                 "ESRI"))%>%
  #$ means exact match
  dplyr::filter(str_detect(path, 
                           "London_Ward_CityMerged.shp$"))%>%
  dplyr::select(path)%>%
  pull()%>%
  #read in the file in
  st_read()
  
```


##1.2 Get the median price of short-term leases (less than 90 days) from Inside airbnb**
                              
```{r setup, results='hide'}
#use the  September data
InsideAirbnb <- read_csv("http://data.insideairbnb.com/united-kingdom/england/london/2015-09-02/visualisations/listings.csv")
#from the coordinate values stored in the x and y columns, which look like they are latitude and longitude values, create a new points dataset
InsideAirbnb_sf <- st_as_sf(InsideAirbnb, 
                           coords = c("longitude","latitude"), 
                           crs = 4326)
# get the rent price(<90 days)
rent_price90 <- InsideAirbnb_sf  %>%
  filter(availability_365<=90) %>%
  dplyr::select("price", "availability_365","geometry") 

# transform to the same crs and join data with Londonwards
rent_price90<- st_transform(rent_price90, 27700)  
Londonwards<- st_transform(Londonwards, 27700)

merge_price <- sf::st_join(rent_price90,Londonwards["GSS_CODE"])

#get the mean_price by ward level
median_price <- merge_price   %>% 
  group_by(GSS_CODE)%>%
  summarise(mean_price=median(price))
mean_price<- merge_price   %>% group_by(GSS_CODE)%>%
  summarise(mean_price=mean(price))
####it shows that some wards don't have data
``` 

it shows that some wards don't have data, so I decide to add the April Airbnb data is added to the September data to extract the median price again.

``` {r setup, results='hide'}
##it airbnb September data plus April data, "2015-listings.csv" is the sum 
InsideAirbnb3 <- read_csv("2015-listings.csv")
InsideAirbnb3_sf <- st_as_sf(InsideAirbnb3, 
                           coords = c("longitude","latitude"), 
                           crs = 4326) %>%
                           st_transform(., 27700)  
# get the rent price(<90 days)
rent_price90_3 <- InsideAirbnb3_sf  %>%
  filter(availability_365<=90) %>%
  dplyr::select("price", "availability_365","geometry") 

merge_price3 <- sf::st_join(rent_price90_3,Londonwards["GSS_CODE"])

#get the mean_price by ward level
median_price3 <- merge_price3   %>% group_by(GSS_CODE)%>%
  summarise(median_price=median(price))

```                              
  
                                          
##1.3 Aggregate independent variable data
```{r setup, results='hide'}
crime =read.csv("MPS_Ward_Level_Crime_Historic_NewWard.csv", 
               header = TRUE, sep = ",", encoding = "latin1")%>% 
      group_by(WardCode)%>%
      summarise(crime2015=sum(Crime2015))

accessibility=read.csv("Ward2011 AvPTAI2015.csv", 
             header = TRUE, sep = ",", encoding = "latin1")

wardprofile2015=read.csv("ward-profiles-excel-version.csv", 
                                               header = TRUE, sep = ",", encoding = "latin1")
variables <- crime %>%  
  left_join(., 
            accessibility,
            by = c("WardCode" = "WardCode"))
variables<- variables %>%  
  left_join(., 
            wardprofile2015,
            by = c("WardCode" = "WardCode"))
variables<- variables %>%  
  clean_names() 

#create a new csv
write.table(variables,"variables.csv",row.names=FALSE,col.names=TRUE,sep=",")
```

##1.4 merge boundaries and variables
```{r setup, results='hide'}
#londonward with indenpent variables
LonWard_variables <- Londonwards%>%
  left_join(.,
            variables, 
            by = c("GSS_CODE" = "ward_code"))
  
#with airbnb data         
 LonWard_variables <-sf::st_join(LonWard_variables,median_price3["median_price"])      

```

##1.5 mapping the dependent variable 
```{r}
tmap_mode("view")
qtm(LonWard_variables, 
    fill = "median_price", 
    borders = NULL,  
    fill.palette = "Blues")+
  tm_scale_bar(position = c("left", "bottom"))+
  tm_compass(position = c("right", "top"),type = "arrow") 

  
```
   
   
#**Part 2：OLS Regression
   
##2.1 descriptive statistics
```{r}
#Clean the dataset
LonWard_variables <- LonWard_variables  %>%
  dplyr::select("ward_name","GSS_CODE" ,"geometry","median_price","crime2015", "av_ptai2015", "house_price_gap","claimant_rate_of_housing_benefit_2015") 

#check the distribution of these variables first

p1<-ggplot(LonWard_variables, aes(x=median_price)) + 
  geom_histogram(aes(y = ..density..),
                 binwidth = 5) + 
  geom_density(colour="red", 
               size=1, 
               adjust=1)
p2<-ggplot(LonWard_variables, aes(x=crime2015)) + 
  geom_histogram(aes(y = ..density..),
                 binwidth = 5) + 
  geom_density(colour="red", 
               size=1, 
               adjust=1)
p3<-ggplot(LonWard_variables, aes(x=av_ptai2015)) + 
  geom_histogram(aes(y = ..density..),
                 binwidth = 5) + 
  geom_density(colour="red", 
               size=1, 
               adjust=1)
p4<-ggplot(LonWard_variables, aes(x=house_price_gap)) + 
  geom_histogram(aes(y = ..density..),
                 binwidth = 5) + 
  geom_density(colour="red", 
               size=1, 
               adjust=1)
p5<-ggplot(LonWard_variables, aes(x=claimant_rate_of_housing_benefit_2015)) + 
  geom_histogram(aes(y = ..density..),
                 binwidth = 5) + 
  geom_density(colour="red", 
               size=1, 
               adjust=1)
multiplot(p1, p2, p3, p4,p5,cols=2)
```

```{r}
#tranformation----house_price_gap
symbox(~house_price_gap, 
       LonWard_variables, 
       na.rm=T,
       powers=seq(-3,3,by=.5))
```
```{r}
ggplot(LonWard_variables, aes(x=(house_price_gap)^0.5)) + 
  geom_histogram()
```
   
##2.2 Simple linear regression
```{r}
LonWard_variables_dropna<-na.omit(LonWard_variables)
Regressiondata<- LonWard_variables_dropna%>%
  dplyr::select(median_price, 
                crime2015)
model1 <- Regressiondata %>%
  lm(median_price ~
               crime2015,
     data=.)

#av_ptai2015
Regressiondata2<- LonWard_variables_dropna%>%
  dplyr::select(median_price, 
                av_ptai2015)
model2 <- Regressiondata2 %>%
  lm(median_price ~
               av_ptai2015,
     data=.)

#house_price_gap
LonWard_variables_dropna<-LonWard_variables_dropna%>%
  mutate(house_price_gap_transform= ((house_price_gap)^0.5))
         
Regressiondata3<- LonWard_variables_dropna%>%
  dplyr::select(median_price, 
                house_price_gap_transform)
model3 <- Regressiondata3 %>%
  lm(median_price ~
               house_price_gap_transform,
     data=.)


Regressiondata4<- LonWard_variables_dropna%>%
  dplyr::select(median_price, 
                claimant_rate_of_housing_benefit_2015)
model4 <- Regressiondata4 %>%
  lm(median_price ~
               claimant_rate_of_housing_benefit_2015,
     data=.)
summary(model1)
summary(model2)
summary(model3)
summary(model4)
```
It is obvious that there is no correlation in house_price_gap and crime with short-term rental prices. So we focus on av_ptai2015 and claimant_rate_of_housing_benefit_2015, and check the residuals to see  if it meets the linear regression conditions.

```{r}

model_data2 <- model2 %>%
  augment(., Regressiondata2)

model_data4 <- model4 %>%
  augment(., Regressiondata4)
#plot residuals
p1 <-model_data2%>%
dplyr::select(.resid)%>%
  pull()%>%
  qplot()+ 
geom_histogram(aes(y = ..density..),
                 binwidth = 5)  
  

p2 <-model_data4%>%
dplyr::select(.resid)%>%
  pull()%>%
  qplot()+ 
geom_histogram(aes(y = ..density..),
                 binwidth = 5)   

multiplot(p1, p2,cols=2)
```

##2.2 multiple linear regression
```{r}
multipleRegression<- LonWard_variables_dropna%>%
  clean_names()%>%
  dplyr::select(median_price,
         av_ptai2015,
         claimant_rate_of_housing_benefit_2015)

multiplemodel <- lm(median_price ~ av_ptai2015 + 
               claimant_rate_of_housing_benefit_2015, data = multipleRegression)

#show the summary of those outputs
tidy(multiplemodel)
glance(multiplemodel)
```

###check VIF and residual
```{r}
vif(multiplemodel)

multiplemodel_data <- multiplemodel %>%
  augment(., multipleRegression)

# also add them to the shapelayer
LonWard_variables_dropna <- LonWard_variables_dropna %>%
  mutate(multipleRegressionresids = residuals(multiplemodel))

#print some model diagnositcs. 
par(mfrow=c(2,2))    #plot to 2 by 2 array
plot(multiplemodel)
```

##2.3 Autocorrelation
```{r}
DW <- durbinWatsonTest(multiplemodel)
tidy(DW)
```
```{r}
#now plot the residuals
tmap_mode("view")
#qtm(LonWardProfiles, fill = "model1_resids")

tm_shape(LonWard_variables_dropna) +
  tm_polygons("multipleRegressionresids",
              palette = "RdYlBu") +
  tm_scale_bar(position = c("left", "bottom"))+
  tm_compass(position = c("right", "bottom"),type = "arrow") 

  #par(new = TRUE)
 # tm_shape(Londonwards)
```
###Moran's I
```{r}
#calculate the centroids of all Wards in London
coordsW <- LonWard_variables_dropna%>%
  st_centroid()%>%
  st_geometry()

# generate a spatial weights matrix. We'll start with a simple binary matrix of queen's case neighbours

LWard_nb <- LonWard_variables_dropna %>%
  poly2nb(., queen=T)

#or nearest neighbours
knn_wards <-coordsW %>%
  knearneigh(., k=4)

LWard_knn <- knn_wards %>%
  knn2nb()

#create a spatial weights matrix object from these weights
Lward.queens_weight <- LWard_nb %>%
   #if no-neighbour observations were present and the zero.policy argument set to true.
  nb2listw(.,style="C",zero.policy=TRUE)

Lward.knn_4_weight <- LWard_knn %>%
  nb2listw(.,style="C",zero.policy=TRUE)

Queen <- LonWard_variables_dropna %>%
  st_drop_geometry()%>%
  dplyr::select(multipleRegressionresids)%>%
  pull()%>%
  moran.test(., Lward.queens_weight,zero.policy=TRUE)%>%
  tidy()

Nearest_neighbour <-  LonWard_variables_dropna %>%
  st_drop_geometry()%>%
  dplyr::select(multipleRegressionresids)%>%
  pull()%>%
  moran.test(., Lward.knn_4_weight,zero.policy=TRUE)%>%
  tidy()

Queen
```

```{r}
Nearest_neighbour
```

##2.4 GWR 
```{r}
library(spgwr)
st_crs(LonWard_variables_dropna) = 27700
LonWard_variablesSP <- LonWard_variables_dropna %>%
  as(., "Spatial")

st_crs(coordsW) = 27700
coordsWSP <- coordsW %>%
  as(., "Spatial")

#calculate kernel bandwidth
GWRbandwidth <- gwr.sel(median_price ~ av_ptai2015 + 
               claimant_rate_of_housing_benefit_2015, 
                  data = LonWard_variablesSP, 
                        coords=coordsWSP,
                        adapt=T)
#run the gwr model
gwr.model = gwr(median_price ~ av_ptai2015 + 
               claimant_rate_of_housing_benefit_2015, 
                  data = LonWard_variablesSP, 
                coords=coordsWSP, 
                adapt=GWRbandwidth, 
                hatmatrix=TRUE, 
                se.fit=TRUE)

results <- as.data.frame(gwr.model$SDF)
names(results)

#attach coefficients to original SF
LonWardProfiles2 <- LonWard_variables_dropna %>%
  mutate(coefAccessibility = results$av_ptai2015,
         coefBenefit = results$claimant_rate_of_housing_benefit_2015)
#mapping
tmap_mode("view")
tm_shape(LonWardProfiles2) +
  tm_polygons(col = "coefAccessibility", 
              palette = "RdBu", 
              alpha = 0.5)+
    tm_scale_bar(position = c("left", "bottom"))+
  tm_compass(position = c("right", "bottom"),type = "arrow") 
```


```{r}
tmap_mode("view")
tm_shape(LonWardProfiles2) +
  tm_polygons(col = "coefBenefit", 
              palette = "RdBu", 
              alpha = 0.5)+ 
    tm_scale_bar(position = c("left", "bottom"))+
  tm_compass(position = c("right", "bottom"),type = "arrow") 
```


